The \dealii{} Library, Version 9.0

### 2018-04-21 9.0/paper.tex
List sources of support for myself and for Rene.

% W.~Bangerth was partially
% supported by the National Science Foundation under award OCI-1148116
% as part of the Software Infrastructure for Sustained Innovation (SI2)
% program; and by the Computational Infrastructure in Geodynamics initiative
% (CIG), through the National Science Foundation under Awards
% No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.

>>>>

W.~Bangerth and R.~Gassm\"{o}ller were partially
supported by the National Science Foundation under award OCI-1148116
as part of the Software Infrastructure for Sustained Innovation (SI2)
program; and by the Computational Infrastructure in Geodynamics initiative
(CIG), through the National Science Foundation under Awards
No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.
